### 2016-08-22 architecture.tex
Clarify and cleanup str/repr footnote. Add a \ref to the srepr section.
Add a dedicated paragraph about Speed
And move all SymEngine discussio in there. The conclusion was simplified.

\subsection{The Core}

A computer algebra system stores mathematical expressions as data
structures.  For example, the mathematical expression $x + y$ is represented as
a tree with three nodes, $+$, $x$, and $y$, where $x$ and $y$ are ordered
children of $+$.  As users manipulate
mathematical expressions with traditional mathematical syntax, the CAS
manipulates the underlying data structures.  Automated optimizations and
computations such as integration, simplification, etc.\ are all functions that
consume and produce expression trees.

@@

>>>>

\subsection{The Core}
\label{sec:core}
A computer algebra system stores mathematical expressions as data
structures.  For example, the mathematical expression $x + y$ is represented as
a tree with three nodes, $+$, $x$, and $y$, where $x$ and $y$ are ordered
children of $+$.  As users manipulate
mathematical expressions with traditional mathematical syntax, the CAS
manipulates the underlying data structures.  Automated optimizations and
computations such as integration, simplification, etc.\ are all functions that
consume and produce expression trees.

@@

\subsection{Speed}

Due to being written in pure Python, SymPy's speed is generally slower compared
with its commercial competitors. For many applications and uses of SymPy, that
is not a problem, as SymPy is able to return the answer quickly enough, but for
some applications that require handling of very long expressions and/or lots of
small expressions, the speed becomes a problem.

For this reason, a new library called SymEngine~\cite{SymEngine} was started.
It is a pure C++ library with thin wrappers to other languages (Python, Ruby,
Julia, ...) whose aim is to be the fastest manipulation library.  Preliminary
benchmarks suggest that SymEngine is as fast or faster than the commercial or
open source competitors.

SymPy recently started to use SymEngine as an optional backend, initially in
\texttt{sympy.mechanics} only. The plan is to allow more algorithms in SymPy to
take advantage of the speed of SymEngine.

### 2016-08-22 conclusion_and_future_work.tex
Add a dedicated paragraph about Speed
And move all SymEngine discussio in there. The conclusion was simplified.

Some of the planned future work for SymPy includes work on improving code
generation, improvements to the speed of SymPy (one area of work in this
direction is \href{https://github.com/symengine/symengine}{SymEngine}, a
C++ symbolic manipulation library that is planned to be usable as a
alternative core for SymPy), improving the assumptions system, and improving the
solvers submodule.

>>>>

Some of the planned future work for SymPy includes work on improving code
generation, improvements to the speed of SymPy using SymEngine, improving the
assumptions system, and improving the solvers submodule.
